Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-23 article.tex
wording Damien + references

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}

@@

As the first plot in Figure~\ref{fig:filtered-signal} illustrates, the raw
fluorescence signal is very noisy due to light scattering artifacts that
ordinarily affects the quality of the recording~\citep{lichtman2011big}.
Accordingly, the first step of our pipeline is to smoothen the signal, using
one the following low-pass filter for filtering out high frequency noise :
\begin{align}
% symmetrical median filter
f_1(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i,
\label{eq:weighted-asymetric-median}
\end{align}
where $f_1$x effect is shown in the second plot in the figure.

Considering the short delay of communication between neurons and the slow
decay of fluorescence, the second step of our pipeline consists in identifying
neuron spikes -- characterized by high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the third plot of the figure:
\begin{align} % an asymmetrical discrete derivative filter
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

Once the low- and and high-pass filters have been applied, the remaining signal
corresponds to the discrete derivative of the fluorescence time series. To
further filter out small signal variations, mostly due to noise, the third step
consists in a  hard-threshold filter, yielding the fourth plot in the figure:
\begin{align}
h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0.
\end{align}

@@

In those terms, the full signal processing pipeline of our (simplified)
approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
(resp. $f_2$ for the winning method).

>>>>

\begin{figure}
\centering
\subfigure[Raw signal]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass filter $f_1$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass filter $g$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Hard-threshold filter $h$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Global regularization $w$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:weight_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}

@@

As the Figure~\ref{fig:original_curve} illustrates, the raw
fluorescence signal is very noisy due to light scattering artifacts that
ordinarily affects the quality of the recording~\citep{lichtman2011big}.
Accordingly, the first step of our pipeline is to smoothen the signal, using
one the following low-pass filter for filtering out high frequency noise :
\begin{align}
% symmetrical median filter
f_1(x^t_i) &= x^{t-1}_i + x^t_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
f_2(x^t_i) &= 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_i^t,
\label{eq:weighted-asymetric-median}
\end{align}
where $f_1$ effect is shown in Figure \ref{fig:lp_curve}.

Considering the short delay of communication between neurons and the slow
decay of fluorescence, the second step of our pipeline consists in identifying
neuron spikes -- characterized by high frequencies -- by filtering out low
frequencies through a high-pass filter, resulting in the plot of
Figure \ref{fig:hp_curve}:
\begin{align}
g(x^{t}_{i}) &= x^{t}_i - x^{t-1}_i. \label{eq:high-pass-filter}
\end{align}

Once the low- and and high-pass filters have been applied, the remaining signal
corresponds to the finite backward difference of the fluorescence time series.
To further filter out small signal variations, mostly due to noise, the third
step consists in a  hard-threshold filter, yielding the Figure
\ref{fig:threshold_curve}:
\begin{align}
h(x^{t}_i) &= x^{t}_i \mathbb{1}(x^{t}_i \geq \tau) \text{ with } \tau > 0.
\end{align}

@@

In those terms, the full signal processing pipeline of our (simplified)
approach is defined by the composed function $w \cdot h \cdot g \cdot f_1$
(resp. $f_2$) and results in the plot of Figure \ref{fig:weight_curve}.
